Incentivizing Exploration with Unbiased Histories

### 2019-04-29 ec19 workshops/cover-straregic-learning.tex
Added a bit more.

Prior work achieves much progress with disclosure policies that merely recommend an action to each user, without any other supporting information, and sometimes recommend exploratory actions. (Absent agents' incentives, such policy is a multi-armed bandit algorithm.) All this work relies heavily on trust and rationality assumptions, standard in economic theory. However, these assumptions are quite problematic in the context of the motivating applications such as recommendation systems. It is very unclear whether users would know and understand some complicated disclosure policy announced  by the principal, let alone trust the principal to faithfully implement this policy. Even if they do know the policy and trust that it was implemented as claimed, it's unclear whether users would react to it rationally, particularly regarding the possibility of being singled out for exploration.

>>>>

Prior work achieves much progress with disclosure policies that merely recommend an action to each user, without any other supporting information, and sometimes recommend exploratory actions. (Absent agents' incentives, such policy is a multi-armed bandit algorithm.) All this work relies heavily on trust and rationality assumptions, standard in economic theory. However, these assumptions are quite problematic in the context of the motivating applications such as recommendation systems. It is very unclear whether users would know and understand some complicated disclosure policy announced  by the principal, let alone trust the principal to faithfully implement this policy. (The principal may deviate from the announced policy either intentionally, or due to insufficient information about the users, or because of bugs in implementation.) Even if the users understand the policy and trust that it was implemented as claimed, it's unclear whether users would react to it rationally, particularly regarding the lack of supporting information and the possibility of being singled out for exploration. For example, users may find such disclosure policies unacceptable and leave the system.
